---
title: "data_uploadsFinal"
author: "Kevin Gilds"
date: "Thursday, August 13, 2015"
output:
  html_document:
    toc: yes
---

```{r}

library(sqldf)
library(reshape2)
library(dplyr)
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")
getRealdb<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")



```


# Data from 2014-2015 MY Year. 

## Matched Data

### Girl Survey Pre Post upload to Sqlite. 

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

girl_pre_post <- read.csv("prePost081315.csv")


dbWriteTable(conn = getRealdb, name = "girl_pre_post_matched", value= girl_pre_post, row.names=FALSE, overwrite=TRUE)


```

### Upload Reading Grades to Sqlite Matched

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

reading_final <- readRDS("reading_final.rds")

dbWriteTable(conn = getRealdb, name = "reading_final_matched", value= reading_final, row.names=FALSE, overwrite=TRUE)





```


#### Langarts Final to Sqlite Matched

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

langarts_final <- readRDS("langarts_final.rds")

dbWriteTable(conn = getRealdb, name = "langarts_final_matched", value= langarts_final, row.names=FALSE, overwrite=TRUE)






```


### Attendance Data  Matched

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")


##### REad the RDS data
absences_final <- readRDS("absences_final.rds")

dbWriteTable(conn = getRealdb, name = "absences_final", value= absences_final, row.names=FALSE, overwrite=TRUE)






```


### Behavior Data  Matched

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

behavior_data <-readRDS("behavior_final.rds")

dbWriteTable(conn = getRealdb, name = "behavior_data", value= behavior_data, row.names=FALSE, overwrite=TRUE)





```



### Matched Suspensions

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")


suspensions <-readRDS("final_suspensions.rds")

dbWriteTable(conn = getRealdb, name = "matched_suspenions", value= suspensions, row.names=FALSE, overwrite=TRUE)

```



###  Pre Teacher Survey All Matched

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/teacher")

pre_teacher <- readRDS("preTeacher.rds")

dbWriteTable(conn = getRealdb, name = "pre_teacher", value= pre_teacher, row.names=FALSE, overwrite=TRUE)




```


## 2014-2015 All data entry

### Girl Survey Pre Survey

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015")

pre_girl_survey <- readRDS("girlPre07042015.rds")

dbWriteTable(conn = getRealdb, name = "pre_girl_survey", value= pre_girl_survey, row.names=FALSE, overwrite=TRUE)


```


### Post Survey Post Survey

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015")

post_girl_survey <- readRDS("girlPost07042015.rds")


dbWriteTable(conn = getRealdb, name = "post_girl_survey", value= post_girl_survey, row.names=FALSE, overwrite=TRUE)




```



### Post Teacher Survey All 

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/teacher")

post_teacher <- readRDS("postTeacher.rds")

dbWriteTable(conn = getRealdb, name = "post_teacher", value= post_teacher, row.names=FALSE, overwrite=TRUE)

```

### Pre Parent Survey All

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/parent")

pre_parent <- readRDS("preParent")

dbWriteTable(conn = getRealdb, name = "pre_parent", value= pre_parent, row.names=FALSE, overwrite=TRUE)


```


### Post Parent Survey All

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/parent")

post_parent <- readRDS("postParent1.rds")

dbWriteTable(conn = getRealdb, name = "postParent", value= post_parent, row.names=FALSE, overwrite=TRUE)



```



### Quarter 1 Reading

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades")

q1_reading <-readRDS("quarter1reading.rds")

dbWriteTable(conn = getRealdb, name = "q1_reading", value= q1_reading, row.names=FALSE, overwrite=TRUE)





```

### Quarter 1 Lang Arts


```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades")

q1_langarts <-readRDS("quarter1Lang.rds")

dbWriteTable(conn = getRealdb, name = "q1_Langarts", value= q1_langarts, row.names=FALSE, overwrite=TRUE)


```

### Quarter 1 Unexcused Absences

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades")

q1_unexcused <-readRDS("q1UnexcusedAbs.rds")

dbWriteTable(conn = getRealdb, name = "q1_unexcused_abs", value= q1_unexcused, row.names=FALSE, overwrite=TRUE)

```


### Quarter 1 Excused Absences

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades")

q1_excused <-readRDS("q1ExcusedAbs.rds")

dbWriteTable(conn = getRealdb, name = "q1_excused_abs", value= q1_excused, row.names=FALSE, overwrite=TRUE)


```


### Quarter 1 Out of School Suspensions

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades")

q1_outOfSchool <-readRDS("q1OutOfSchoolSuspensions.rds")

dbWriteTable(conn = getRealdb, name = "q1_outOfSchool_suspensions", value= q1_outOfSchool, row.names=FALSE, overwrite=TRUE)





```


### Quarter 1 In School Suspensions

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades")

q1_inSchool <-readRDS("q1InSchoolSusp.rds")

dbWriteTable(conn = getRealdb, name = "q1_inSchool_suspensions", value= q1_inSchool, row.names=FALSE, overwrite=TRUE)






```


### Quarter 1 Behavior Referrals

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades")

q1_referrals <-readRDS("q1BehaviorReferrals.rds")

dbWriteTable(conn = getRealdb, name = "q1_behavior_referrals", value= q1_referrals, row.names=FALSE, overwrite=TRUE)




```


### Quarter 1 Expelled

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades")

q1_expelled <- readRDS("q1Expelled.rds")

dbWriteTable(conn = getRealdb, name = "q1_expelled", value= q1_expelled, row.names=FALSE, overwrite=TRUE)





```


### Quarter 2 Reading

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q2")

q2_reading <-readRDS("q2Reading.rds")

dbWriteTable(conn = getRealdb, name = "q2_reading", value= q2_reading, row.names=FALSE, overwrite=TRUE)





```


### Quarter 2 Lang Arts


```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q2")

q2_langarts <-readRDS("q2LangArts.rds")

dbWriteTable(conn = getRealdb, name = "q2_langarts", value= q2_langarts, row.names=FALSE, overwrite=TRUE)


```


### Quarter 2 Unexcused Absences

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q2")

q2_unexcused <-readRDS("q2UnexcusedAbsences.rds")

dbWriteTable(conn = getRealdb, name = "q2_unexcused_abs", value= q2_unexcused, row.names=FALSE, overwrite=TRUE)

```


### Quarter 2 Excused Absences

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q2")

q2_excused <-readRDS("q2ExcusedAbsences.rds")

dbWriteTable(conn = getRealdb, name = "q2_excused_abs", value= q2_excused, row.names=FALSE, overwrite=TRUE)


```


### Quarter 2 Out of School Suspensions

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q2")

q2_outOfSchool <-readRDS("q2OutFinal.rds")

dbWriteTable(conn = getRealdb, name = "q2_outOfSchool_suspensions", value= q2_outOfSchool, row.names=FALSE, overwrite=TRUE)


```


### Quarter 2 In School Suspensions

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q2")

q2_inSchool <-readRDS("q2InSchoolSuspensions.rds")

dbWriteTable(conn = getRealdb, name = "q2_inSchool_suspensions", value= q2_inSchool, row.names=FALSE, overwrite=TRUE)



```

### Quarter 2 Behavior Referrals

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q2")

q2_referrals <-readRDS("q2BehaviorReferral.rds")

dbWriteTable(conn = getRealdb, name = "q2_behavior_referrals", value= q2_referrals, row.names=FALSE, overwrite=TRUE)




```


### Quarter 3 Reading

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q3")

q3_reading <-readRDS("q3Reading.rds")

dbWriteTable(conn = getRealdb, name = "q3_reading", value= q3_reading, row.names=FALSE, overwrite=TRUE)


```


### Quarter 3 Lang Arts


```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q3")

q3_langarts <-readRDS("q3LangArts.rds")

dbWriteTable(conn = getRealdb, name = "q3_langarts", value= q3_langarts, row.names=FALSE, overwrite=TRUE)


```


### Quarter 3 Unexcused Absences

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q3")

q3_unexcused <-readRDS("q3unExcusedAbs.rds")

dbWriteTable(conn = getRealdb, name = "q3_unexcused_abs", value= q3_unexcused, row.names=FALSE, overwrite=TRUE)

```


### Quarter 3 Excused Absences

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q3")

q3_excused <-readRDS("q3ExcusedAbs.rds")

dbWriteTable(conn = getRealdb, name = "q3_excused_abs", value= q3_excused, row.names=FALSE, overwrite=TRUE)


```





### Quarter 3 In School Suspsenions

### Quarter 3 Behavior Referrals



```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q3")

q3_referrals <-readRDS("q3BehavRef.rds")

dbWriteTable(conn = getRealdb, name = "q3_behavior_referrals", value= q3_referrals, row.names=FALSE, overwrite=TRUE)




```


### Quarter 4 Reading

```{r}

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q4")

q4_reading <-readRDS("q4Reading.rds")

dbWriteTable(conn = getRealdb, name = "q4_reading", value= q4_reading, row.names=FALSE, overwrite=TRUE)


```


### Quarter 4 Language Arts

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q4")

q4_langarts <-readRDS("q4LangArtsFinal.rds")

dbWriteTable(conn = getRealdb, name = "q4_langarts", value= q4_langarts, row.names=FALSE, overwrite=TRUE)


```


### Quarter 4 Unexcused Absences

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q4")

q4_unexcused <-readRDS("q4UnexecusedAbsFinal.rds")

dbWriteTable(conn = getRealdb, name = "q4_unexcused_abs", value= q4_unexcused, row.names=FALSE, overwrite=TRUE)

```


### Quarter 4 Excused Absneces

```{r}


setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q4")

q4_excused <-readRDS("q4ExcusedAbsFinal.rds")

dbWriteTable(conn = getRealdb, name = "q4_excused_abs", value= q4_excused, row.names=FALSE, overwrite=TRUE)

```


### Quarter 4 Out of School Suspensions

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q4")

q4_outOfSchool <-readRDS("q4AOutOfSchoolSuspensions.rds")

dbWriteTable(conn = getRealdb, name = "q4_outOfSchool_suspensions", value= q4_outOfSchool, row.names=FALSE, overwrite=TRUE)


```


### Quarter 4 In School Suspenions


```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q4")

q4_inSchool <-readRDS("q4InSchoolSuspensionsFinal.rds")

dbWriteTable(conn = getRealdb, name = "q4_inSchool_suspensions", value= q4_inSchool, row.names=FALSE, overwrite=TRUE)



```


### Quarter4 Expelled

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q4")

q4_expelled <- readRDS("q4Expelled.rds")

dbWriteTable(conn = getRealdb, name = "q4_expelled", value= q4_expelled, row.names=FALSE, overwrite=TRUE)


```


### Quarter 4 Prompoted

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/July 2015/grades/q4")

promoted <- readRDS("q4Promoted.rds")

dbWriteTable(conn = getRealdb, name = "q4_promoted", value= promoted, row.names=FALSE, overwrite=TRUE)


```

